---
title: "Homework 5"
author: "Sarah McLarnan"
date: 2019-11-04
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

### Problem 1

```{r data load, message = FALSE}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r data_clean}
clean_iris = function(x) {
  
   if (is.numeric(x)) {
   replace_na(x, mean(x, na.rm = TRUE))
   }
   else if (is.character(x)) 
     {replace_na(x, "virginica")}
}

output = map_dfr(.x = iris_with_missing, ~ clean_iris(.x))
output %>%
  view()
```

### Problem 2

```{r problem 2}
names_df =
  tibble(
  subject = list.files(path="./data")
)
file_path = "./data/"
file_names = file_path %>%
  list.files()
observations_df =
  file_names %>%
  map_dfr(function(file_name){
 
  read_csv(paste0(file_path, file_name))
})
study_data = cbind(names_df, observations_df) %>%
 mutate(subject = str_replace(subject, ".csv", "")) %>%
 pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations")
study_data %>%
  ggplot(aes(x = as.numeric(week), y = observations, color = subject)) +
  geom_line() +
  labs(title = "Weekly observations by subject", x = "Week", y = "Observation Value") + theme(legend.position = "bottom")
```

On average the experimental group had higher observed values than the control group, especially in later weeks. 

### Problem 3

```{r regression simulation}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 50)
  )
  
  ls_fit = lm(y ~ x, data = sim_data) %>%
     broom::tidy() %>%
     select(term, estimate, p.value)
  
}
sim_results = 
  tibble(beta1 = 0:6) %>% 
  mutate(
    output_lists = purrr::map(.x = beta1, ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_dfs = purrr::map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```


```{r plot 1}
sim_results %>%
  group_by(beta1) %>%
  summarize(n = n(),
            prop_sig = sum(p.value < .05)/n()*100) %>%
  ggplot(aes(x = beta1, y = prop_sig)) + geom_point() + geom_smooth(se = FALSE) + labs(x = "Beta1", y = "Proportion of Null Rejected", title = "Proportion of Times Null Rejected by Beta1")
```

Plot 1 shows a positive non-linear assocation between Beta1 and the proportion of times the null was rejected. 

```{r plot 2}
sim_results %>%
  group_by (beta1) %>%
  summarize (average_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = average_estimate)) + geom_point() + geom_line() + labs(x = "Beta1", y = "Mean Estimate Beta1", title = "Mean Estimated Beta1 vs True Beta1")
```

```{r plot 3}
sim_results %>%
  filter(p.value < .05) %>% 
  group_by(beta1) %>%
  summarize (average_estimate = mean(estimate)) %>%
  ggplot(aes(x = beta1, y = average_estimate)) + geom_point() + geom_line()  + labs(x = "Beta1", y = "Mean Estimate Beta1", title = "Mean Estimated Beta1 vs True Beta1 when p<0.05") 
```

The average estimated Beta 1 does not approximate the true Beta1 for tests in which the null was rejected. This is because the cases in which the null was rejected are those that are significantly different from the truth (i.e. the true B1). The significant tests tend to overestimate the true beta1. 